---
title: "Tidyverse EXTEND - Magnus' code"
author: "Dominika Markowska-Desvallons"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



### Load tidyverse library



```{r}
library(tidyverse)
```


### Read .csv and display data

After downloading the .csv file from Kaggle and uploading it to Github, we read the corresponding data (in raw form) and then familiarize ourselves with the dataset by displaying column names and the 1st 6 observations.

```{r}
#Read .csv data
happy_alc <- read_csv("https://raw.githubusercontent.com/Magnus-PS/CUNY-SPS-DATA-607/tidyverse/HappinessAlcoholConsumption.csv")

#Familiarize ourselves with the dataset
colnames(happy_alc)
view(happy_alc)

```
### Select columns by name
You want to return a “subset” of columns from your data frame by listing the name of each column to return.
```{r}
happy_alc %>% 
  select(Country,HappinessScore)

```

### Select a range of columns
You want to return two columns from a data frame as well as every column that appears between them.

```{r}
happy_alc %>% 
  select(Country:HDI)
```
### Select columns by integer position
You want to return a “subset” of columns from your data frame by listing the position of each column to return.

```{r}
happy_alc %>% 
  select(1, 3, 6)
```
### Insights 
I decidded to extend Magnus code by transforming his dataset with couple recipes of 'select', because as almost always tables are made of multiple data stuctures that work together 
The table itself is a data frame or tibble.
The columns are vectors.
Some columns may be list-columns, which are lists that contain vectors.
To transform a table, I  begin with a code - select by name, select range of columns and select columns by integer position that transforms the structure of the table. 


### Explore ggplot2



```{r}
#Take the sum of 3 columns (Beer_PerCapita, Spirit_PerCapita, and Wine_PerCapita) to form 1 column: Total
happy_alc_rev <- happy_alc %>%
    mutate(TotalAlc = select(., Beer_PerCapita:Wine_PerCapita) %>% rowSums(na.rm = TRUE))

ggplot(happy_alc_rev, aes(x=HappinessScore, y=TotalAlc, color=Region)) + 
  geom_point() +
  labs(title = "Alcohol Consumption vs. Happiness", subtitle = "(A visualization by region for 122 nations)", x = "Happiness Score", y = "Total Alcohol Consumption") +
  geom_smooth(method=lm, color = "black")

```


