
---
title: "TidyVerse Extended"
output: html_document
author: "Zhouxin Shi"
date: "2020-11-08"
---

Overall:23/25
I think this part , "Write a vignette using more than one TidyVerse packages" is missing in your work.
get data from 538 
It looks like typo...I think you are getting data from fivethirtyeight
```{r}
library("dplyr")
source = 'https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/master/covid_approval_polls.csv'
#read data into data frame
df <- read.csv(source)

#I think the above 02 line can be resume with one as follow below
df <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/master/covid_approval_polls.csv")
df
#I think maybe looking at data details can help you shape your approach
str(df)
#the dimension of the data: 2008 obs. of  13 variables:

```

Demonstrate functions in tidyverse package dplyr
```{r}
library("dplyr")
#Relocate changes the order of the columns
#the first argument should be the data set, the 2nd is the column you want to move, the third is a how you want to move it.  For this, i chose .after, which will place it after the specific column chosen for this parameter.
new_df = relocate(df, pollster, .after = start_date)
new_df
#count counts observations by group
#the first argument should be the data set, the 2nd is the column you want to group by, and the third is if you want to sort or not.
count(new_df, population, sort=TRUE)
```

### Extended 
Since this vignette is using dplyr, we will extend this work by adding 
other different functions of dplyr (filter,summarize,arrange )

- filter()

```{r}
new_df %>%
    filter(sponsor!="")
```

- summarize()
```{r}
df2 <- new_df %>%
  group_by(population) %>%
  summarize(average_approve = 
              sum(approve, na.rm = TRUE) / n())
df2
```
- arrange()
```{r}
df2 %>%
    arrange(desc(average_approve))%>%
    head(20)
```


Demonstrate functions in tidyverse package ggplot2
```{r}
library("ggplot2")
# Create a scatter plot
#the first argument should be the data set, the 2nd is the x axis variable, and the third is the y axis variable.
# Maybe including the title
ggplot(new_df, aes(x=population, y=sample_size)) + geom_bar(stat="identity")
```
